Articles Of Association

### 2014-11-17 Articles_of_Association_Melbourne_Bitcoin_Technology_Centre_MBTC_2015.tex
Fix grammar and escape chevrons
Add geographic designator to 'The Act' in definition

  The regulations as were in force upon the date of adoption of these Articles shall apply to the Association save to the extent that they are excluded by or are inconsistent with any of these Articles.
  \linebreak[1]
  \\This is free and unencumbered material is released into the public domain.
  \linebreak[1]
  \\Anyone is free to copy, modify, publish, use, compile, sell, or
  distribute this content, either in source code form or as a compiled
  binary, for any purpose, commercial or non-commercial, and by any
  means.
  \linebreak[1]
  \\In jurisdictions that recognize copyright laws, the author or authors
  of this content dedicate any and all copyright interest in the
  material to the public domain. We make this dedication for the benefit
  of the public at large and to the detriment of our heirs and
  successors. We intend this dedication to be an overt act of
  relinquishment in perpetuity of all present and future rights to this
  content under copyright law.
  \linebreak[1]
  \\THE MATERIAL IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
  EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
  MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
  IN NO EVENT SHALL THE AUTHORS BE LIABLE FOR ANY CLAIM, DAMAGES OR
  OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE,
  ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
  OTHER DEALINGS IN THE CONTENTS.
  \linebreak[1]
  \\For more information, please refer to <http://unlicense.org>

@@

      \item{} ``\emph{the Act}'' means the Associations Incorporation Reform Act 
      2012 including the Associations Incorporation Reform Regulations 2012;

>>>>

  The regulations as were in force upon the date of adoption of these Articles shall apply to the Association save to the extent that they are excluded by or are inconsistent with any of these Articles.
  \linebreak[1]
  \\This material is free and unencumbered material is released into the public domain.
  \linebreak[1]
  \\Anyone is free to copy, modify, publish, use, compile, sell, or
  distribute this content, either in source code form or as a compiled
  binary, for any purpose, commercial or non-commercial, and by any
  means.
  \linebreak[1]
  \\In jurisdictions that recognize copyright laws, the author or authors
  of this content dedicate any and all copyright interest in the
  material to the public domain. We make this dedication for the benefit
  of the public at large and to the detriment of our heirs and
  successors. We intend this dedication to be an overt act of
  relinquishment in perpetuity of all present and future rights to this
  content under copyright law.
  \linebreak[1]
  \\THE MATERIAL IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
  EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
  MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
  IN NO EVENT SHALL THE AUTHORS BE LIABLE FOR ANY CLAIM, DAMAGES OR
  OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE,
  ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
  OTHER DEALINGS IN THE CONTENTS.
  \linebreak[1]
  \\For more information, please refer to \<http://unlicense.org\>

@@

      \item{} ``\emph{the Act}'' means the Associations Incorporation Reform Act 2012, Victoria, Australia including the Associations Incorporation Reform Regulations 2012;
